\section{Speaker / Lecture / Workshop / Events}\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        {\emph{Coliving Conference}, Speaker} \\
        {Amsterdam, The Netherlands, Sep. 2023} \\
    }}
    \small{\item{
        {\emph{Lecture/Workshop}, Royal Academy of Art (KABK)} \\
        {Den Haag, The Netherlands, Jan. 2023} \\
    }}
    \small{\item{
        {\emph{Speaker}, EGI Conference} \\
        {Amsterdam, The Netherlands, Nov. 2020} \\
    }}
    \small{\item{
        {\emph{Speaker}, IMPAKT Festival} \\
        {Utrecht, The Netherlands, Oct. 2020} \\
    }}
    \small{\item{
        {\emph{Speaker}, Gateways Conference, Science Gateways Community Institute (SGCI)} \\
        {San Diego, CA, USA, Oct. 2020} \\
    }}
    \small{\item{
        {\emph{Lecture/Workshop}, Aalto University} \\
        {Helsinki, Finland, Dec. 2019} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Mutation Festival} \\
        {Nerdlab, Ghent, Belgium, Oct. 2019} \\
    }}
    \small{\item{
        {\emph{Participant}, Sandberg Instituut Masterclass} \\
        {Amsterdam, The Netherlands, Mar. 2019} \\
    }}
    \small{\item{
        {\emph{Workshop/Exhibitor}, Science Gateways Community Institute (SGCI)} \\
        {San Diego, CA, USA, Sep. 2018} \\
    }}
    \small{\item{
        {\emph{Organizer}, Hackers \& Designers Summer Academy 2018} \\
        {Amsterdam, The Netherlands, Jul. 2018} \\
    }}
    \small{\item{
        {\emph{Lecture/Workshop}, School of City Design, CAFA} \\
        {Beijing, China, Oct. 2017} \\
    }}
    \small{\item{
        {\emph{Lecture/Workshop}, Fine Arts Academy of Hunan Normal University} \\
        {Chang Sha, China, Oct. 2017} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Oddstream} \\
        {Arnhem, The Netherlands, Oct. 2017} \\
    }}
    \small{\item{
        {\emph{Organizer}, Hackers \& Designers Summer Academy 2017} \\
        {Amsterdam, The Netherlands, Jul. 2017} \\
    }}
    \small{\item{
        {\emph{Speaker}, FIBER Festival, Speaker} \\
        {Amsterdam, The Netherlands, May 2017} \\
    }}
    \small{\item{
        {\emph{Speaker}, Hackers \& Founders Meetup} \\
        {Amsterdam, The Netherlands, Apr. 2017} \\
    }}
    \small{\item{
        {\emph{Speaker}, REMEDI Pump collaborative conference} \\
        {Chicago, IL, USA, Apr. 2017} \\
    }}
    \small{\item{
        {\emph{Residency}, Oddstream Oddstay} \\
        {Arnhem, The Netherlands, Apr. 2017} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, STRP Festival} \\
        {Eindhoven, The Netherlands, Mar. 2017} \\
    }}
    \small{\item{
        {\emph{Workshop}, Baby you can drive my car (self-driving car)} \\
        {Amsterdam, The Netherlands, Feb. 2017} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, KASK, ... een kleptomaan neemt de dingen letterlijk ...,} \\
        {Gent, Belgium, Feb. 2017} \\
    }}
    \small{\item{
        {\emph{Workshop}, Big Brother Awards} \\
        {Amsterdam, The Netherlands, Nov. 2016} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Journey with Hovel Bot} \\
        {Brussels, Belgium, Oct. 2016} \\
    }}
    \small{\item{
        {\emph{Speaker}, ACM Purdue University} \\
        {West Lafayette, IN, USA, Oct. 2016} \\
    }}
    \small{\item{
        {\emph{Workshop}, Endless Cities Festival} \\
        {Toronto, Canada, Sep. 2016} \\
    }}
    \small{\item{
        {\emph{Speaker}, Otis College} \\
        {Los Angeles, CA, USA, Sep. 2016} \\
    }}
    \small{\item{
        {\emph{Residency}, Mad Scientist Festival} \\
        {Bern, Switzerland, Sep. 2016} \\
    }}
    \small{\item{
        {\emph{Organizer}, Hackers \& Designers Summer Academy 2016} \\
        {Amsterdam, The Netherlands, Jul. 2016} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Northside Festival} \\
        {Brooklyn, NY, USA, June 2016} \\
    }}
    \small{\item{
        {\emph{Speaker/Exhibitor}, Sektor 3.0 Conference} \\
        {Warsaw, Poland, May 2016} \\
    }}
    \small{\item{
        {\emph{Workshop}, LibreGraphics Meetup} \\
        {London, United Kingdom, Apr. 2016} \\
    }}
    \small{\item{
        {\emph{Workshop}, Sandberg Instituut} \\
        {Amsterdam, The Netherlands, Feb. 2016} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, ZineFest} \\
        {Berlin, Germany, Nov. 2015} \\
    }}
    \small{\item{
        {\emph{Workshop}, Mozilla Mozfest} \\
        {London, United Kingdom, Oct. 2015} \\
    }}
    \small{\item{
        {\emph{Speaker}, EBF Conference} \\
        {Groningen, The Netherlands, September 2015} \\
    }}
    \small{\item{
        {\emph{Organizer}, Hackers \& Designers Summer Academy 2015} \\
        {Amsterdam, The Netherlands, Jul. 2015} \\
    }}
    \small{\item{
        {\emph{Residency}, Invisible Cities Festival} \\
        {Gorizia, Italy, June 2015} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Appril Festival} \\
        {Amsterdam, The Netherlands, Mar. 2015} \\
    }}
    \small{\item{
        {\emph{Workshop}, University of Amsterdam} \\
        {Amsterdam, The Netherlands, Feb. 2015} \\
    }}
    \small{\item{
        {\emph{Workshop}, Mozilla Mozfest} \\
        {London, United Kingdom, Oct. 2014} \\
    }}
    \small{\item{
        {\emph{Exhibitor}, Collision Conference} \\
        {Las Vegas, NV, USA, May 2014} \\
    }}
    \small{\item{
        {\emph{Exhibitor/Speaker}, Tech Crunch Disrupt} \\
        {Berlin, Germany, Oct. 2013} \\
    }}
    \small{\item{
        {\emph{\ldots}}
    }}
 \end{itemize}


